---
title: "GOseq_heatmap_kazu's_way"
output: html_document
---


```{r}
library(ShortRead);library(goseq);library(GO.db);library("annotate")
```
```{r}
getwd()
At_cdna<-Biostrings::readDNAStringSet("../reference/TAIR10_cdna_20110103_representative_gene_model_updated.1")
At_cdna

```


```{r}
Atgoslim.TAIR<-read_tsv("../reference/ATH_GO_GOSLIM.txt",skip=2,col_names = FALSE )
```

```{r}
head(Atgoslim.TAIR)
Atgoslim.TAIR %>% filter(X8=="P",X1=="AT4G38360") %>% dplyr::select(1,5,6,8,9,10)###what does this mean? means BP  biological process
Atgoslim.TAIR.BP <-Atgoslim.TAIR%>% filter(X8=="P")
head(Atgoslim.TAIR.BP)
Atgoslim.TAIR.BP.list<-tapply(Atgoslim.TAIR.BP$X6,Atgoslim.TAIR.BP$X1,c)
head(Atgoslim.TAIR.BP.list)
save(Atgoslim.TAIR.BP.list, list,file=file.path("../output","Atgoslim.TAIR.BP.list.Rdata"))

Atgoslim.TAIR.CC <-Atgoslim.TAIR%>% filter(X8=="C")
head(Atgoslim.TAIR.CC)
Atgoslim.TAIR.CC.list<-tapply(Atgoslim.TAIR.CC$X6,Atgoslim.TAIR.CC$X1,c)
head(Atgoslim.TAIR.CC.list)
save(Atgoslim.TAIR.CC.list, list,file=file.path("../output","Atgoslim.TAIR.CC.list.Rdata"))
```
#import expressed genes 

```{r}
expressed.genes <- read_csv("../output/expressed_genes_counts.csv")
expressed.genes <- expressed.genes$target_id
expressed.genes <- as.data.frame(expressed.genes)
head(expressed.genes)
colnames(expressed.genes) <- "gene_id"
expressed.genes$gene_id <- gsub("\\.\\d", "", expressed.genes$gene_id)
head(expressed.genes)
```



```{r}
GOseq.Atgoslim.BP.list.ORA<-function(genelist,padjust=0.05,ontology="BP",custom.category.list=Atgoslim.TAIR.BP.list,cdna=At_cdna,expressed.genes=expressed.genes) { # return GO enrichment table, padjus, padjust=0.05. 
  bias<-nchar(cdna)#to get the length of each gene
  names(bias)<-tibble(AGI=names(cdna)) %>% separate(AGI,into="AGI2",pattern="|",extra="drop") %>% dplyr::select(AGI2) %>% as_vector()# to get the AGI of each gene
  table(duplicated(names(bias)))# to see if there is duplicated AGI
  #TF<-(names(bias) %in% genelist)*1
  bias <- bias[names(bias)%in%expressed.genes$gene_id] # use only expressed genes in the experiment as reference
  TF<-as.integer(names(bias) %in% genelist)
  names(TF)<-names(bias)
  #print(TF)
  pwf<-nullp(TF,bias.data=bias)
  #print(pwf$DEgenes)
  GO.pval <- goseq(pwf,gene2cat=custom.category.list,use_genes_without_cat=TRUE) # format became different in new goseq version (021111). Does not work (042716)
  #head(GO.pval) 
  if(ontology=="BP") {
    GO.pval2<-subset(GO.pval,ontology=="BP")
  } else if(ontology=="CC") {
    GO.pval2<-subset(GO.pval,ontology=="CC")
  } else {
    GO.pval2<-subset(GO.pval,ontology=="MF")
  }
  # calculating padjust by BH  
  GO.pval2$over_represented_padjust<-p.adjust(GO.pval2$over_represented_pvalue,method="BH")
  if(GO.pval2$over_represented_padjust[1]>padjust) return("no enriched GO")
  else {
    enriched.GO<-GO.pval2[GO.pval2$over_represented_padjust<padjust,] 
    print("enriched.GO is")
    print(enriched.GO)
    
    ## write Term and Definition 
    for(i in 1:dim(enriched.GO)[1]) {
      if(is.null(Term(GOTERM[enriched.GO[i,"category"]]))) {next} else {
      enriched.GO$Term[i]<-Term(GOTERM[[enriched.GO[i,"category"]]])
      enriched.GO$Definition[i]<-Definition(GOTERM[[enriched.GO[i,"category"]]])
      }
    }
    return(enriched.GO)
  }
}

```



#for shade regulated genes in Col at 1 and 49 hour treatment, not consider the interaction
```{r}
#1h
DEgene.Col.1h <- read.csv("../output/DEgenes.Col.1h.sep.csv")
head(DEgene.Col.1h)
colnames(DEgene.Col.1h)[1] <- "gene_id"
head(DEgene.Col.1h)
DEgene.Col.1h$gene_id <- gsub("\\.\\d", "", DEgene.Col.1h$gene_id)
head(DEgene.Col.1h)
shade1h.up.Col <- DEgene.Col.1h%>% filter(logFC > 0)
shade1h.down.Col <- DEgene.Col.1h%>% filter(logFC < 0)
GOseq.Atgoslim.BP.list.ORA(genelist=shade1h.up.Col$gene_id, expressed.genes = expressed.genes)
GOseq.Atgoslim.BP.list.ORA(genelist=shade1h.down.Col$gene_id, expressed.genes = expressed.genes)

GOseq.Atgoslim.BP.list.ORA(ontology="CC",custom.category.list=Atgoslim.TAIR.CC.list, genelist=shade1h.up.Col$gene_id, expressed.genes = expressed.genes)
GOseq.Atgoslim.BP.list.ORA(ontology="CC",custom.category.list=Atgoslim.TAIR.CC.list, genelist=shade1h.down.Col$gene_id, expressed.genes = expressed.genes)
```

```{r}
#49h
DEgene.Col.49h <- read.csv("../output/DEgenes.Col.49h.sep.csv")
head(DEgene.Col.49h)
colnames(DEgene.Col.49h)[1] <- "gene_id"
head(DEgene.Col.49h)
DEgene.Col.49h$gene_id <- gsub("\\.\\d", "", DEgene.Col.49h$gene_id)
head(DEgene.Col.49h)
shade49h.up.Col <- DEgene.Col.49h%>% filter(logFC > 0)
shade49h.down.Col <- DEgene.Col.49h%>% filter(logFC < 0)
GOseq.Atgoslim.BP.list.ORA(genelist=shade49h.up.Col$gene_id, expressed.genes = expressed.genes)
GOseq.Atgoslim.BP.list.ORA(genelist=shade49h.down.Col$gene_id, expressed.genes = expressed.genes)

GOseq.Atgoslim.BP.list.ORA(ontology="CC",custom.category.list=Atgoslim.TAIR.CC.list, genelist=shade49h.up.Col$gene_id, expressed.genes = expressed.genes)
GOseq.Atgoslim.BP.list.ORA(ontology="CC",custom.category.list=Atgoslim.TAIR.CC.list, genelist=shade49h.down.Col$gene_id, expressed.genes = expressed.genes)
```

#for shade regulated genes in myc234 at 1 and 49 hour treatment, not consider the interaction
```{r}
#1h
DEgene.myc234.1h <- read.csv("../output/DEgenes.myc234.1h.sep.csv")
head(DEgene.myc234.1h)
colnames(DEgene.myc234.1h)[1] <- "gene_id"
head(DEgene.myc234.1h)
DEgene.myc234.1h$gene_id <- gsub("\\.\\d", "", DEgene.myc234.1h$gene_id)
head(DEgene.myc234.1h)
shade1h.up.myc234 <- DEgene.myc234.1h%>% filter(logFC > 0)
shade1h.down.myc234 <- DEgene.myc234.1h%>% filter(logFC < 0)
GOseq.Atgoslim.BP.list.ORA(genelist=shade1h.up.myc234$gene_id, expressed.genes = expressed.genes)
GOseq.Atgoslim.BP.list.ORA(genelist=shade1h.down.myc234$gene_id, expressed.genes = expressed.genes)

GOseq.Atgoslim.BP.list.ORA(ontology="CC",custom.category.list=Atgoslim.TAIR.CC.list, genelist=shade1h.up.myc234$gene_id, expressed.genes = expressed.genes)
GOseq.Atgoslim.BP.list.ORA(ontology="CC",custom.category.list=Atgoslim.TAIR.CC.list, genelist=shade1h.down.myc234$gene_id, expressed.genes = expressed.genes)
```

```{r}
#49h
DEgene.myc234.49h <- read.csv("../output/DEgenes.myc234.49h.sep.csv")
head(DEgene.myc234.49h)
colnames(DEgene.myc234.49h)[1] <- "gene_id"
head(DEgene.myc234.49h)
DEgene.myc234.49h$gene_id <- gsub("\\.\\d", "", DEgene.myc234.49h$gene_id)
head(DEgene.myc234.49h)
shade49h.up.myc234 <- DEgene.myc234.49h%>% filter(logFC > 0)
shade49h.down.myc234 <- DEgene.myc234.49h%>% filter(logFC < 0)
GOseq.Atgoslim.BP.list.ORA(genelist=shade49h.up.myc234$gene_id, expressed.genes = expressed.genes)
GOseq.Atgoslim.BP.list.ORA(genelist=shade49h.down.myc234$gene_id, expressed.genes = expressed.genes)

GOseq.Atgoslim.BP.list.ORA(ontology="CC",custom.category.list=Atgoslim.TAIR.CC.list, genelist=shade49h.up.myc234$gene_id, expressed.genes = expressed.genes)
GOseq.Atgoslim.BP.list.ORA(ontology="CC",custom.category.list=Atgoslim.TAIR.CC.list, genelist=shade49h.down.myc234$gene_id, expressed.genes = expressed.genes)
```

#for shade regulated genes in npr at 1 and 49 hour treatment, not consider the interaction
```{r}
#1h
DEgene.npr.1h <- read.csv("../output/DEgenes.npr.1h.sep.csv")
head(DEgene.npr.1h)
colnames(DEgene.npr.1h)[1] <- "gene_id"
head(DEgene.npr.1h)
DEgene.npr.1h$gene_id <- gsub("\\.\\d", "", DEgene.npr.1h$gene_id)
head(DEgene.npr.1h)
shade1h.up.npr <- DEgene.npr.1h%>% filter(logFC > 0)
shade1h.down.npr <- DEgene.npr.1h%>% filter(logFC < 0)
GOseq.Atgoslim.BP.list.ORA(genelist=shade1h.up.npr$gene_id, expressed.genes = expressed.genes)
GOseq.Atgoslim.BP.list.ORA(genelist=shade1h.down.npr$gene_id, expressed.genes = expressed.genes)

GOseq.Atgoslim.BP.list.ORA(ontology="CC",custom.category.list=Atgoslim.TAIR.CC.list, genelist=shade1h.up.npr$gene_id, expressed.genes = expressed.genes)
GOseq.Atgoslim.BP.list.ORA(ontology="CC",custom.category.list=Atgoslim.TAIR.CC.list, genelist=shade1h.down.npr$gene_id, expressed.genes = expressed.genes)

```

```{r}
#49h
DEgene.npr.49h <- read.csv("../output/DEgenes.npr.49h.sep.csv")
head(DEgene.npr.49h)
colnames(DEgene.npr.49h)[1] <- "gene_id"
head(DEgene.npr.49h)
DEgene.npr.49h$gene_id <- gsub("\\.\\d", "", DEgene.npr.49h$gene_id)
head(DEgene.npr.49h)
shade49h.up.npr <- DEgene.npr.49h%>% filter(logFC > 0)
shade49h.down.npr <- DEgene.npr.49h%>% filter(logFC < 0)
GOseq.Atgoslim.BP.list.ORA(genelist=shade49h.up.npr$gene_id, expressed.genes = expressed.genes)
GOseq.Atgoslim.BP.list.ORA(genelist=shade49h.down.npr$gene_id, expressed.genes = expressed.genes)

GOseq.Atgoslim.BP.list.ORA(ontology="CC",custom.category.list=Atgoslim.TAIR.CC.list, genelist=shade49h.up.npr$gene_id, expressed.genes = expressed.genes)
GOseq.Atgoslim.BP.list.ORA(ontology="CC",custom.category.list=Atgoslim.TAIR.CC.list, genelist=shade49h.down.npr$gene_id, expressed.genes = expressed.genes)
```




#for shade regulated genes in sid at 1 and 49 hour treatment, not consider the interaction
```{r}
#1h
DEgene.sid.1h <- read.csv("../output/DEgenes.sid.1h.sep.csv")
head(DEgene.sid.1h)
colnames(DEgene.sid.1h)[1] <- "gene_id"
head(DEgene.sid.1h)
DEgene.sid.1h$gene_id <- gsub("\\.\\d", "", DEgene.sid.1h$gene_id)
head(DEgene.sid.1h)
shade1h.up.sid <- DEgene.sid.1h%>% filter(logFC > 0)
shade1h.down.sid <- DEgene.sid.1h%>% filter(logFC < 0)
GOseq.Atgoslim.BP.list.ORA(genelist=shade1h.up.sid$gene_id, expressed.genes = expressed.genes)
GOseq.Atgoslim.BP.list.ORA(genelist=shade1h.down.sid$gene_id, expressed.genes = expressed.genes)

GOseq.Atgoslim.BP.list.ORA(ontology="CC",custom.category.list=Atgoslim.TAIR.CC.list, genelist=shade1h.up.sid$gene_id, expressed.genes = expressed.genes)
GOseq.Atgoslim.BP.list.ORA(ontology="CC",custom.category.list=Atgoslim.TAIR.CC.list, genelist=shade1h.down.sid$gene_id, expressed.genes = expressed.genes)
```

```{r}
#49h
DEgene.sid.49h <- read.csv("../output/DEgenes.sid.49h.sep.csv")
head(DEgene.sid.49h)
colnames(DEgene.sid.49h)[1] <- "gene_id"
head(DEgene.sid.49h)
DEgene.sid.49h$gene_id <- gsub("\\.\\d", "", DEgene.sid.49h$gene_id)
head(DEgene.sid.49h)
shade49h.up.sid <- DEgene.sid.49h%>% filter(logFC > 0)
shade49h.down.sid <- DEgene.sid.49h%>% filter(logFC < 0)
GOseq.Atgoslim.BP.list.ORA(genelist=shade49h.up.sid$gene_id, expressed.genes = expressed.genes)
GOseq.Atgoslim.BP.list.ORA(genelist=shade49h.down.sid$gene_id, expressed.genes = expressed.genes)

GOseq.Atgoslim.BP.list.ORA(ontology="CC",custom.category.list=Atgoslim.TAIR.CC.list, genelist=shade49h.up.sid$gene_id, expressed.genes = expressed.genes)
GOseq.Atgoslim.BP.list.ORA(ontology="CC",custom.category.list=Atgoslim.TAIR.CC.list, genelist=shade49h.down.sid$gene_id, expressed.genes = expressed.genes)
```



#for the interaction, for myc234, Col and H as refference

```{r}
#1h
DEgene.myc234.1h <- read.csv("../output/DEgenes.myc234.1h.csv")
head(DEgene.myc234.1h)
colnames(DEgene.myc234.1h)[1] <- "gene_id"
head(DEgene.myc234.1h)
DEgene.myc234.1h$gene_id <- gsub("\\.\\d", "", DEgene.myc234.1h$gene_id)
head(DEgene.myc234.1h)
shade1h.up.myc234 <- DEgene.myc234.1h%>% filter(logFC.gtmyc234 > 0)
shade1h.down.myc234 <- DEgene.myc234.1h%>% filter(logFC.gtmyc234 < 0)
GOseq.Atgoslim.BP.list.ORA(genelist=shade1h.up.myc234$gene_id, expressed.genes = expressed.genes)
GOseq.Atgoslim.BP.list.ORA(genelist=shade1h.down.myc234$gene_id, expressed.genes = expressed.genes)


GOseq.Atgoslim.BP.list.ORA(ontology="CC",custom.category.list=Atgoslim.TAIR.CC.list, genelist=shade1h.up.myc234$gene_id, expressed.genes = expressed.genes)
GOseq.Atgoslim.BP.list.ORA(ontology="CC",custom.category.list=Atgoslim.TAIR.CC.list, genelist=shade1h.down.myc234$gene_id, expressed.genes = expressed.genes)

```

```{r}
#49h
DEgene.myc234.49h <- read.csv("../output/DEgenes.myc234.49h.csv")
head(DEgene.myc234.49h)
colnames(DEgene.myc234.49h)[1] <- "gene_id"
head(DEgene.myc234.49h)
DEgene.myc234.49h$gene_id <- gsub("\\.\\d", "", DEgene.myc234.49h$gene_id)
head(DEgene.myc234.49h)
shade49h.up.myc234 <- DEgene.myc234.49h%>% filter(logFC.gtmyc234 > 0)
shade49h.down.myc234 <- DEgene.myc234.49h%>% filter(logFC.gtmyc234 < 0)
GOseq.Atgoslim.BP.list.ORA(genelist=shade49h.up.myc234$gene_id, expressed.genes = expressed.genes)
GOseq.Atgoslim.BP.list.ORA(genelist=shade49h.down.myc234$gene_id, expressed.genes = expressed.genes)

GOseq.Atgoslim.BP.list.ORA(ontology="CC",custom.category.list=Atgoslim.TAIR.CC.list, genelist=shade49h.up.myc234$gene_id, expressed.genes = expressed.genes)
GOseq.Atgoslim.BP.list.ORA(ontology="CC",custom.category.list=Atgoslim.TAIR.CC.list, genelist=shade49h.down.myc234$gene_id, expressed.genes = expressed.genes)
```

#for npr, interaction, Col and L as reference
```{r}
#1h
DEgene.npr.1h <- read.csv("../output/DEgenes.npr.1h.csv")
head(DEgene.npr.1h)
colnames(DEgene.npr.1h)[1] <- "gene_id"
head(DEgene.npr.1h)
DEgene.npr.1h$gene_id <- gsub("\\.\\d", "", DEgene.npr.1h$gene_id)
head(DEgene.npr.1h)
shade1h.up.npr <- DEgene.npr.1h%>% filter(logFC.gtnpr > 0)
shade1h.down.npr <- DEgene.npr.1h%>% filter(logFC.gtnpr < 0)
GOseq.Atgoslim.BP.list.ORA(genelist=shade1h.up.npr$gene_id, expressed.genes = expressed.genes)
GOseq.Atgoslim.BP.list.ORA(genelist=shade1h.down.npr$gene_id, expressed.genes = expressed.genes)

GOseq.Atgoslim.BP.list.ORA(ontology="CC",custom.category.list=Atgoslim.TAIR.CC.list, genelist=shade1h.up.npr$gene_id, expressed.genes = expressed.genes)
GOseq.Atgoslim.BP.list.ORA(ontology="CC",custom.category.list=Atgoslim.TAIR.CC.list, genelist=shade1h.down.npr$gene_id, expressed.genes = expressed.genes)

```

```{r}
#49h
DEgene.npr.49h <- read.csv("../output/DEgenes.npr.49h.csv")
head(DEgene.npr.49h)
colnames(DEgene.npr.49h)[1] <- "gene_id"
head(DEgene.npr.49h)
DEgene.npr.49h$gene_id <- gsub("\\.\\d", "", DEgene.npr.49h$gene_id)
head(DEgene.npr.49h)
shade49h.up.npr <- DEgene.npr.49h%>% filter(logFC.gtnpr > 0)
shade49h.down.npr <- DEgene.npr.49h%>% filter(logFC.gtnpr < 0)
GOseq.Atgoslim.BP.list.ORA(genelist=shade49h.up.npr$gene_id, expressed.genes = expressed.genes)
GOseq.Atgoslim.BP.list.ORA(genelist=shade49h.down.npr$gene_id, expressed.genes = expressed.genes)

GOseq.Atgoslim.BP.list.ORA(ontology="CC",custom.category.list=Atgoslim.TAIR.CC.list, genelist=shade49h.up.npr$gene_id, expressed.genes = expressed.genes)
GOseq.Atgoslim.BP.list.ORA(ontology="CC",custom.category.list=Atgoslim.TAIR.CC.list, genelist=shade49h.down.npr$gene_id, expressed.genes = expressed.genes)
```

#for sid , interaction

```{r}
#1h
DEgene.sid.1h <- read.csv("../output/DEgenes.sid.1h.csv")
head(DEgene.sid.1h)
colnames(DEgene.sid.1h)[1] <- "gene_id"
head(DEgene.sid.1h)
DEgene.sid.1h$gene_id <- gsub("\\.\\d", "", DEgene.sid.1h$gene_id)
head(DEgene.sid.1h)
shade1h.up.sid <- DEgene.sid.1h%>% filter(logFC.gtsid > 0)
shade1h.down.sid <- DEgene.sid.1h%>% filter(logFC.gtsid < 0)
GOseq.Atgoslim.BP.list.ORA(genelist=shade1h.up.sid$gene_id, expressed.genes = expressed.genes)
GOseq.Atgoslim.BP.list.ORA(genelist=shade1h.down.sid$gene_id, expressed.genes = expressed.genes)

GOseq.Atgoslim.BP.list.ORA(ontology="CC",custom.category.list=Atgoslim.TAIR.CC.list, genelist=shade1h.up.sid$gene_id, expressed.genes = expressed.genes)
GOseq.Atgoslim.BP.list.ORA(ontology="CC",custom.category.list=Atgoslim.TAIR.CC.list, genelist=shade1h.down.sid$gene_id, expressed.genes = expressed.genes)
```

```{r}
#49h
DEgene.sid.49h <- read.csv("../output/DEgenes.sid.49h.csv")
head(DEgene.sid.49h)
colnames(DEgene.sid.49h)[1] <- "gene_id"
head(DEgene.sid.49h)
DEgene.sid.49h$gene_id <- gsub("\\.\\d", "", DEgene.sid.49h$gene_id)
head(DEgene.sid.49h)
shade49h.up.sid <- DEgene.sid.49h%>% filter(logFC.gtsid > 0)
shade49h.down.sid <- DEgene.sid.49h%>% filter(logFC.gtsid < 0)
GOseq.Atgoslim.BP.list.ORA(genelist=shade49h.up.sid$gene_id, expressed.genes = expressed.genes)
GOseq.Atgoslim.BP.list.ORA(genelist=shade49h.down.sid$gene_id, expressed.genes = expressed.genes)

GOseq.Atgoslim.BP.list.ORA(ontology="CC",custom.category.list=Atgoslim.TAIR.CC.list, genelist=shade49h.up.sid$gene_id, expressed.genes = expressed.genes)
GOseq.Atgoslim.BP.list.ORA(ontology="CC",custom.category.list=Atgoslim.TAIR.CC.list, genelist=shade49h.down.sid$gene_id, expressed.genes = expressed.genes)
```



```{r}
#this is the gene list for the shade regulated genes in different genotype, not consider the interaction
DGE.OBJ1 <- list.files(path=file.path("..","output"), pattern = "\\.sep\\.csv")

#this is the gene list for the differentially expressed genes in different genotype by using Col as reference
DGE.OBJ2 <- list.files(path=file.path("..","output"), pattern = "^DEgenes\\.[^Col&].+h\\.csv")

DEG.objs <- c(DGE.OBJ1, DGE.OBJ2)

DEG.objs2 <- list.files(path=file.path("..","output"), pattern = ".rH\\.csv")
```


```{r}
# read csv file
DEG.list<-lapply(DEG.objs2, function(x) read_csv(paste(file.path("..","output"),"/",x,sep="")))
names(DEG.list)<-gsub(".csv","",DEG.objs)
DEG.list

```

```{r}
# single coefficient
names(DEG.list)
```

```{r}
for(n in 1:8) {
library(dplyr)
  #genelist.up<-base::get(paste("../output/",DEG.objs.V1.5annotation.unique[n],sep="")) %>% rownames_to_column() %>%  dplyr::filter(logFC>0) # does not work
    genelist.up<-DEG.list[[n]]  %>%  dplyr::filter(logFC>0)
    genelist.down<-DEG.list[[n]] %>%  dplyr::filter(logFC<0)
    GO.ORA.temp.up<-GOseq.Atgoslim.BP.list.ORA(gsub("\\.[[:digit:]]+", "", as_vector(genelist.up[,"X1"])),custom.category.list=Atgoslim.TAIR.BP.list, expressed.genes = expressed.genes) 
    GO.ORA.temp.down<-GOseq.Atgoslim.BP.list.ORA(gsub("\\.[[:digit:]]+", "", as_vector(genelist.down[,"X1"])),custom.category.list=Atgoslim.TAIR.BP.list, expressed.genes = expressed.genes) 
# handling "no enriched GO" 
    # genelist.names<-c("GO.ORA.temp.up_down","GO.ORA.temp.down_up") # test
    x<-list(GO.ORA.temp.up=GO.ORA.temp.up,
            GO.ORA.temp.down=GO.ORA.temp.down) # list
    x<-x[!x=="no enriched GO"] # reove "no enriched GO" result
    ## add sample info and FC info and save GO.ORA result
     if (length(x)!=0){ 
    for (i in 1:length(x)) {
        
      GO.ORA.result<-x[[i]] %>% mutate(FC = gsub("(GO.ORA.temp.)(.)","\\2",names(x)[i]),sample=DEG.objs[n])
    save(GO.ORA.result,file=file.path("..","output",paste(gsub(".csv","",DEG.objs[n]),gsub("(GO.ORA.temp.)(.)","\\2",names(x)[i]),"enrich.Rdata",sep=".")))
    rm(GO.ORA.result)
        
    } 
     }
}
```

```{r}
for(n in 9:14) {
library(dplyr)
  #genelist.up<-base::get(paste("../output/",DEG.objs.V1.5annotation.unique[n],sep="")) %>% rownames_to_column() %>%  dplyr::filter(logFC>0) # does not work
      genelist.all<-DEG.list[[n]]
#     DEG.list[[n]]  %>%  dplyr::select("logFC.genotypenpr1.1")
#         DEG.list[[n]]  %>%  dplyr::select(logFC.genotypenpr1.1)
# 
#         DEG.list[[n]]  %>%  dplyr::select(names(DEG.list[[n]])[2]) %>% filter(.>0)
#         DEG.list[[n]]  %>%  dplyr::filter(names(DEG.list[[n]])[2]>0)
#         DEG.list[[n]]  %>%  dplyr::filter(logFC.genotypenpr1.1>0) # does work
#         DEG.list[[n]]  %>%  dplyr::filter("logFC.genotypenpr1.1">0)
#         DEG.list[[n]]  %>%  dplyr::filter(rlang::UQ("logFC.genotypenpr1.1")>0)
#         DEG.list[[n]]  %>%  dplyr::filter(!!"logFC.genotypenpr1.1">0)
#         DEG.list[[n]]  %>%  dplyr::filter(!!names(DEG.list[[n]])[2]>0)
#         DEG.list[[n]]  %>%  dplyr::filter((!!names(DEG.list[[n]])[2])==3.26)
#         DEG.list[[n]]  %>%  dplyr::filter((!!names(DEG.list[[n]])[2])<0)
#         DEG.list[[n]]  %>%  dplyr::filter((UQ(as.name(names(DEG.list[[n]])[2])))>0) # works! See https://stackoverflow.com/questions/27197617/filter-data-frame-by-character-column-name-in-dplyr
# DEG.list[[n]]  %>%  dplyr::filter((as.name(names(DEG.list[[n]])[2]))>0)  # does not work
genelist.upup<-DEG.list[[n]] %>% dplyr::filter((UQ(as.name(names(DEG.list[[n]])[2])))>0) %>% dplyr::filter((UQ(as.name(names(DEG.list[[n]])[3])))>0)
    genelist.updown<-DEG.list[[n]] %>% dplyr::filter((UQ(as.name(names(DEG.list[[n]])[2])))>0) %>% dplyr::filter((UQ(as.name(names(DEG.list[[n]])[3])))<0)
        genelist.downup<-DEG.list[[n]] %>% dplyr::filter((UQ(as.name(names(DEG.list[[n]])[2])))<0) %>% dplyr::filter((UQ(as.name(names(DEG.list[[n]])[3])))>0)
    genelist.downdown<-  DEG.list[[n]] %>% dplyr::filter((UQ(as.name(names(DEG.list[[n]])[2])))<0) %>% dplyr::filter((UQ(as.name(names(DEG.list[[n]])[3])))<0)
    GO.ORA.temp.all<-GOseq.Atgoslim.BP.list.ORA(gsub("\\.[[:digit:]]+", "", as_vector(genelist.all[,"X1"])),custom.category.list=Atgoslim.TAIR.BP.list, expressed.genes = expressed.genes)
    GO.ORA.temp.up_up<-GOseq.Atgoslim.BP.list.ORA(gsub("\\.[[:digit:]]+", "", as_vector(genelist.upup[,"X1"])),custom.category.list=Atgoslim.TAIR.BP.list, expressed.genes = expressed.genes)
    GO.ORA.temp.up_down<-GOseq.Atgoslim.BP.list.ORA(gsub("\\.[[:digit:]]+", "", as_vector(genelist.updown[,"X1"])),custom.category.list=Atgoslim.TAIR.BP.list, expressed.genes = expressed.genes)
    GO.ORA.temp.down_up<-GOseq.Atgoslim.BP.list.ORA(gsub("\\.[[:digit:]]+", "", as_vector(genelist.downup[,"X1"])),custom.category.list=Atgoslim.TAIR.BP.list, expressed.genes = expressed.genes)
    GO.ORA.temp.down_down<-GOseq.Atgoslim.BP.list.ORA(gsub("\\.[[:digit:]]+", "", as_vector(genelist.downdown[,"X1"])),custom.category.list=Atgoslim.TAIR.BP.list, expressed.genes = expressed.genes)
    # handling "no enriched GO" 
    # genelist.names<-c("GO.ORA.temp.up_down","GO.ORA.temp.down_up") # test
    x<-list(GO.ORA.temp.all=GO.ORA.temp.all,
      GO.ORA.temp.up_up=GO.ORA.temp.up_up,
            GO.ORA.temp.up_down=GO.ORA.temp.up_down,
            GO.ORA.temp.down_up=GO.ORA.temp.down_up,
            GO.ORA.temp.down_down=GO.ORA.temp.down_down) # list
    print(x[x=="no enriched GO"])
    x<-x[!x=="no enriched GO"] # reove "no enriched GO" result
    if (length(x)!=0) {
    ## add sample info and FC info and save GO.ORA result
  for (i in 1:length(x)) {
      GO.ORA.result<-x[[i]] %>% mutate(FC = gsub("(GO.ORA.temp.)(.)","\\2",names(x)[i]),sample=DEG.objs[n])
    save(GO.ORA.result,file=file.path("..","output",paste(gsub(".csv","",DEG.objs[n]),gsub("(GO.ORA.temp.)(.)","\\2",names(x)[i]),"enrich.Rdata",sep=".")))
    rm(GO.ORA.result)
  }
    }
}
```


```{r}
eGOseqs<-list.files(pattern="enrich.Rdata",path=file.path("..","output"))
eGOseqs.list2<-sapply(file.path("..","output",eGOseqs),function(x) mget(load(x))) # mget will return the value of the object(or objects) in a list. see https://stackoverflow.com/questions/29398630/load-data-frames-into-list
#names(eGOseqs.list2)
eGOseqs.list2.summary<-do.call("rbind",eGOseqs.list2) 
#head(eGOseqs.list2.summary) # make sure those are file names
rownames(eGOseqs.list2.summary)<-1:nrow(eGOseqs.list2.summary)
```

```{r}
library(scales)
```

```{r}
# eGOseqs.list2.summary (more than three genes in each KO)
eGOseqs.list2.summary<-eGOseqs.list2.summary[eGOseqs.list2.summary$numDEInCat>3,]
# focused on only very significant GO terms
eGOseqs.list2.summary<-eGOseqs.list2.summary[eGOseqs.list2.summary$over_represented_padjust<0.05,]
# how to cluster GO Ontology according to this pattern?
## using hclust to sort GO terms
GO.list<-unique(eGOseqs.list2.summary$category)
sample.list<-unique(eGOseqs.list2.summary$sample_FC) # revised
# having x-label also used the x-label for df below
eGOseqs.list2.summary <- eGOseqs.list2.summary %>% mutate(sample=gsub(".csv", "", sample)) %>% mutate(sample=gsub(".DEGs.int", "", sample)) %>% unite(sample_FC,sample,FC)

# Making matrix for calculate hierarchical clustering of "over-representd_padjust" value using sperad
df<-eGOseqs.list2.summary %>% dplyr::select(category,sample_FC,over_represented_padjust) %>% spread(sample_FC,over_represented_padjust,-1)

df[df<1e-100]<-1e-100 # to avoid "Inf" after log10 transformation
df<- df %>% mutate_at(vars(2:11) ,.funs=function(x) -log10(x))
# df<- df %>% mutate_at(vars(2:11) ,.funs=-log10) # does not work
df[is.na(df)]<-1
df2<-df[,2:11]
rownames(df2)<-df$category
hc<-stats::hclust(dist(df2), "ave") # only numbers
hc$order
```

```{r}
hc.tib<-tibble(category=hc$labels,order=hc$order)
# change term order using hclust() results
hc.tib2<-hc.tib %>% inner_join(eGOseqs.list2.summary[,c("category","term")],by="category") %>% distinct() %>% arrange(desc(order))
eGOseqs.list2.summary$term<-factor(eGOseqs.list2.summary$term,levels=as_vector(hc.tib2$term))
# To avoid gray color, add 1e-20 to smaller padjust value
eGOseqs.list2.summary$over_represented_padjust[eGOseqs.list2.summary$over_represented_padjust<1e-50]<-1e-50
# format x label
#eGOseqs.list2.summary <- eGOseqs.list2.summary  %>% mutate(sample2=str_replace(sample,"trt.density","trt_density")) %>%  separate(sample2,into=c("tissue","factor","DEGs","model","ref_density","ref_soil"),sep="\\.") %>% mutate(ref_soil=str_remove(ref_soil,"r")) %>% mutate(ref_density=str_remove(ref_density,"r"))  %>% unite(density_FC,ref_density,FC) # simplify elements in "density_FC" column for simpler x label in heatmap
# plot
  GOseq.plot<-ggplot(eGOseqs.list2.summary,aes(x=sample_FC,y=term)) + geom_tile(aes(fill=-log10(over_represented_padjust)),colour="black")  + scale_fill_gradient2(limit=c(0,50),low=muted("green"), high=muted("magenta")) # OK
GOseq.plot<-GOseq.plot+     theme(axis.text.x=element_text(size=10,angle=90),
          axis.text.y=element_text(size=10),
          axis.title=element_text(size=10),
          axis.ticks = element_blank(),
          panel.background = element_rect(fill = "white",colour="black"),
          plot.title=element_text(size=20),
          axis.line=element_blank()) + labs(x="",y="",title="",fill="-log10\n pvalue")
GOseq.plot

ggsave(filename = "GO.enrich.heatmap.pdf", plot = GOseq.plot, path = "../output", height = 20, width = 20,units = "in")
```


#add description for defferetially expressed genes 
```{r}
head(Description.merge)
head (gene.description)
DEG.objs
DEG.list.desc <- DEG.list
names(DEG.list.desc) <- c("DEgenes.Col.1h.rH","DEgenes.Col.49h.rH","DEgenes.myc234.1h.rH","DEgenes.myc234.49h.rH","DEgenes.npr.1h.rH","DEgenes.npr.49h.rH","DEgenes.sid.1h.rH","DEgenes.sid.49h.rH", "DEgenes.myc234.1h.rCol.rH", "DEgenes.myc234.49h.rCol.rH","DEgenes.npr.1h.rCol.rH","DEgenes.npr.49h.rCol.rH","DEgenes.sid.1h.rCol.rH","DEgenes.sid.49h.rCol.rH")

test
```


```{r}
for(n in 1:14){
  test <- DEG.list.desc[[n]]
  colnames(test)[1] <- "gene_id"
    test$gene_id <- gsub("\\.[[:digit:]]+", "", test$gene_id)
    test <- left_join(test, Description.merge, by = "gene_id")
    write.csv(test, file=file.path("../output",paste(names(DEG.list.desc)[n],"csv",sep=".")))
    }
```



