---
title: "MYC234_PIFtargets"
author: "Kazu"
date: "5/22/2019"
output: 
  html_document: 
    keep_md: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,error=TRUE)
```
###package needed
```{r}
library(tidyverse)
library(ggdendro)
library(plotly)
library(edgeR)
library(readxl)
library(goseq) # goseq
```
# PIFtarget list
```{r}
# from tpc120857_SupplementalTable1.pdf (Leivar and Monte, 2014)
PIFup<-c("AT5G39860","AT5G15160","AT4G16780","AT2G44910","AT5G47370","AT3G60390","AT1G18400","AT1G69010","AT1G03790","AT1G02340","AT1G14920","AT2G42870","AT2G46970","AT3G62090","AT2G43060","AT5G02200","AT2G37678","AT1G52830","AT1G04250","AT1G09570","AT4G28720","AT1G04180","AT1G70560","AT4G39950","AT4G27260","AT1G70940","AT3G14370","AT5G18010","AT4G37770","AT5G65800","AT1G02400","AT5G07010","AT5G07000","AT1G75450","AT4G10240","AT4G32280","AT3G15540","AT5G04190","AT4G25470")
PIFdown<-c("AT1G06040","AT5G44190","AT4G26150","AT5G56860","AT5G13630","AT1G70700","AT1G05010","AT5G67030","AT1G01060","AT2G46830")
PIFcomplex<-c("AT5G11260","AT5G02760")
At.PIFtarget.list<-list(PIFup=PIFup,PIFdown=PIFdown,PIFcomplex=PIFcomplex)
```
# convert into custom category list
# prep for GOseq with custom category
```{r}
 # bias.data vector must have the same length as DEgenes vector! 
getwd()
At_cdna<-Biostrings::readDNAStringSet("https://www.arabidopsis.org/download_files/Sequences/TAIR10_blastsets/TAIR10_cdna_20110103_representative_gene_model_updated")
At_cdna
```
# format At.PIFtarget.list2 into goseq() compatible list (run once)
```{r eval=FALSE}
# extract AGI from At_cdna
At.gene.name<-tibble(name=names(At_cdna)) %>% separate(name,into=c("name2","Symbol","description"),sep=" \\|",extra="drop",fill="left") %>%  mutate(AGI=str_remove(name2,pattern="\\.[[:digit:]]+")) 
# make presence/absense hormone responsive gene table (dataframe)
  for(i in 1:3) {
  genes<-At.PIFtarget.list[[i]] %>% as_vector()
  temp<-data.frame(AGI=genes,category=names(At.PIFtarget.list)[i])
  #At.gene.name %>% left_join(temp,by=c("name"="AGI")) -> At.gene.name
At.gene.name %>% left_join(temp,by="AGI") -> At.gene.name 
  }
names(At.gene.name)[5:7] <- names(At.PIFtarget.list)
At.gene.name %>% filter(str_detect(AGI,pattern="AT1G|AT2G|AT3G|AT4G|AT5G|ATC|ATM")) %>% unite(category,5:7,sep=",")->test2
test2[1:10,] %>%  mutate(category=gsub("NA","",category)) %>% mutate(category=gsub(",","",category))
# only select genes with AGI name and concatenate categories
At.gene.name %>% filter(str_detect(AGI,pattern="AT1G|AT2G|AT3G|AT4G|AT5G|ATC|ATM")) %>% unite(category,5:7,sep=",") %>%  mutate(category=gsub("NA,","",category)) %>% mutate(category=gsub(",NA","",category)) %>% mutate(category=gsub("NA","",category)) ->test3
# convert into list object
temp.list<-list()
for(i in 1:dim(test3)[1]) {
  temp.list[[i]]<-test3 %>% slice(i) %>% pull(category)
}
names(temp.list)<-test3 %>% pull(AGI)
# split concatanated categories in each gene
At.PIFtarget.list2<-lapply(temp.list,function(x) unlist(strsplit(x, split=",")))
# save
save(At.PIFtarget.list2,file=file.path("..","output","At.PIFtarget.list2.Rdata"))

```


# prep for GOseq with custom category
```{r}
#  # bias.data vector must have the same length as DEgenes vector! 
# getwd()
# At_cdna<-Biostrings::readDNAStringSet("https://www.arabidopsis.org/download_files/Sequences/TAIR10_blastsets/TAIR10_cdna_20110103_representative_gene_model_updated")
# At_cdna

## if you want to test expressed genes as background, add background in this function
load(file.path("..","output","At.PIFtarget.list2.Rdata"))
GOseq.At.customcat.ORA<-function(genelist,padjust=0.05,custom.category.list=At.hormone.responsive.list,cdna=At_cdna,background="") { # return GO enrichment table, padjus, padjust=0.05. New BLAST2GO results with only BP Brgo.v2.5.BP.list is used (042518). Brgo.v2.5.BP.list is based on Hajar's Blast2go, which should be replaced with Brgo.Atgoslim.BP.list and giving a new name to this function (080818). cdna is DNAstring object. background is a vector of genes.
  #bias<-nchar(cdna)
  bias<-Biostrings::width(cdna)
  # add name to "bias". cdna
  #names(bias)<-names(cdna)
 names(bias) <- tibble(name=names(cdna)) %>% separate(name,into=c("name2","Symbol","description"),sep=" \\|",extra="drop",fill="left") %>%  mutate(AGI=gsub(pattern="\\.[[:digit:]]+", "", name2)) %>% pull(AGI)
 if(background=="") {print("Use all genes in genome as background")} else {
 # select only expressed geens 
  bias <- bias[background$gene_id]
  print("Expessed genes are used as background.")
  print(paste("length of bias is ",length(bias)))
 }
  TF<-(names(bias) %in% genelist)*1
  names(TF)<-names(bias)
  #print(TF)
  pwf<-nullp(TF,bias.data=bias)
  #print(pwf$DEgenes)
  GO.pval <- goseq(pwf,gene2cat=custom.category.list,use_genes_without_cat=TRUE) # format became different in new goseq version (021111). Does not work (042716)
  # calculate p ajust by BH
  GO.pval$over_represented_padjust<-p.adjust(GO.pval$over_represented_pvalue,method="BH")
  if(GO.pval$over_represented_padjust[1]>padjust) return("no enriched GO")
  else {
    enriched.GO<-GO.pval[GO.pval$over_represented_padjust<padjust,] 
    print("enriched.GO is")
    print(enriched.GO)
    return(enriched.GO)
  }
}
```

# Importing enrichment result table and have summary table: Table of DEGs (under construction)
```{r message=FALSE, error=TRUE}
list.files(path=file.path("..","output","DEGs_with_description"),pattern=".csv") # finding files in different blogs did not work.. Did work this time... why?
getwd()
DEG.objs<-list.files(path=file.path("..","output","DEGs_with_description"),pattern="\\.csv$") # under construction
# only Col and myc234
DEG.objs<-grep("(\\.Col|\\.myc234)",DEG.objs,value=TRUE)
# read csv file
DEG.list<-lapply(DEG.objs, function(x) read_csv(paste(file.path("..","output","DEGs_with_description"),"/",x,sep="")))
names(DEG.list)<-gsub(".csv","",DEG.objs)
DEG.list
# GOseq.Atgoslim.BP.list.ORA(genelist=genes.shade1h.up$AGI)
```

# overlap table
```{r}
# expressed genes... what is the best way?
#expressed.genes<- s
#  Col.49h %>% dplyr::select(gene_id) # only 151 genes?
#  gsub("(.)(\\.[[:digit:]]+)","\\1",as_vector(dge.nolow$genes)) # needs to be modified

# testingGOseq.At.customcat 
GOseq.At.customcat.ORA(genelist=At.PIFtarget.list[[1]],custom.category.list=At.PIFtarget.list2)

```
# GO.ORA for each DEG list (loop)
```{r message=FALSE, error=TRUE}
names(DEG.list)
# make special output directory
dir.create(path=file.path("..","output","doubleCoef"))
# for single
for(n in c(1,2,4,6)) {
  genelist.all<-DEG.list[[n]]
  genelist.up<-DEG.list[[n]] %>% dplyr::filter((UQ(as.name(names(DEG.list[[n]])[3])))>0)
  genelist.down<-DEG.list[[n]] %>% dplyr::filter((UQ(as.name(names(DEG.list[[n]])[3])))<0)
  GO.ORA.temp.all<-GOseq.At.customcat.ORA(as_vector(genelist.all[,"gene_id"]),custom.category.list=At.PIFtarget.list2)
    GO.ORA.temp.up<-GOseq.At.customcat.ORA(as_vector(genelist.up[,"gene_id"]),custom.category.list=At.PIFtarget.list2)
    GO.ORA.temp.down<-GOseq.At.customcat.ORA(as_vector(genelist.down[,"gene_id"]),custom.category.list=At.PIFtarget.list2)
    # handling "no enriched GO" 
    # genelist.names<-c("GO.ORA.temp.up_down","GO.ORA.temp.down_up") # test
    x<-list(GO.ORA.temp.all=GO.ORA.temp.all,
      GO.ORA.temp.up=GO.ORA.temp.up,
            GO.ORA.temp.down=GO.ORA.temp.down) # list
    print(x[x=="no enriched GO"])
    x<-x[!x=="no enriched GO"] # reove "no enriched GO" result
    ## add sample info and FC info and save GO.ORA result (this is not working well; 072819)
    ## avoid error with x is empty
    if(length(x)==0) {next} else {
  for (i in 1:length(x)) {
      GO.ORA.result<-x[[i]] %>% mutate(FC = gsub("(GO.ORA.temp.)(.)","\\2",names(x)[i]),sample=DEG.objs[n])
    save(GO.ORA.result,file=file.path("..","output","doubleCoef",paste(gsub(".csv","",DEG.objs[n]),gsub("(GO.ORA.temp.)(.)","\\2",names(x)[i]),"enrich.Rdata",sep=".")))
    rm(GO.ORA.result)
  }
    }
}

# for double coefficint table (needs to fix)
for(n in c(3,5)) {
  genelist.all<-DEG.list[[n]]
# DEG.list[[n]]  %>%  dplyr::filter((as.name(names(DEG.list[[n]])[2]))>0)  # does not work
genelist.upup<-DEG.list[[n]] %>% dplyr::filter((UQ(as.name(names(DEG.list[[n]])[3])))>0) %>% dplyr::filter((UQ(as.name(names(DEG.list[[n]])[4])))>0)
    genelist.updown<-DEG.list[[n]] %>% dplyr::filter((UQ(as.name(names(DEG.list[[n]])[3])))>0) %>% dplyr::filter((UQ(as.name(names(DEG.list[[n]])[4])))<0)
        genelist.downup<-DEG.list[[n]] %>% dplyr::filter((UQ(as.name(names(DEG.list[[n]])[3])))<0) %>% dplyr::filter((UQ(as.name(names(DEG.list[[n]])[4])))>0)
    genelist.downdown<-  DEG.list[[n]] %>% dplyr::filter((UQ(as.name(names(DEG.list[[n]])[3])))<0) %>% dplyr::filter((UQ(as.name(names(DEG.list[[n]])[4])))<0)
#    if(as_vector(genelist.all[,"gene_id"]) ***) { # under construciton. Do not use this form this time.
# if genelist.all[,"gene_id"] has "AT***.1" pattern (with splicing variants)
#GO.ORA.temp.all<-GOseq.At.customcat.ORA(str_remove(as_vector(genelist.all[,"gene_id"]),"\\.[[:digit:]]+"),custom.category.list=At.PIFtarget.list2)
#    GO.ORA.temp.up_up<-GOseq.At.customcat.ORA(str_remove(as_vector(genelist.upup[,"gene_id"]),"\\.[[:digit:]]+"),custom.category.list=At.PIFtarget.list2)
#    GO.ORA.temp.up_down<-GOseq.At.customcat.ORA(str_remove(as_vector(genelist.updown[,"gene_id"]),"\\.[[:digit:]]+"),custom.category.list=At.PIFtarget.list2)
#    GO.ORA.temp.down_up<-GOseq.At.customcat.ORA(str_remove(as_vector(genelist.downup[,"gene_id"]),"\\.[[:digit:]]+"),custom.category.list=At.PIFtarget.list2)
#    GO.ORA.temp.down_down<-GOseq.At.customcat.ORA(str_remove(as_vector(genelist.downdown[,"gene_id"]),"\\.[[:digit:]]+"),custom.category.list=At.PIFtarget.list2)
#    } else {
# if genelist.all[,"gene_id"] has no spricing variant version (only AGI name)
    GO.ORA.temp.all<-GOseq.At.customcat.ORA(as_vector(genelist.all[,"gene_id"]),custom.category.list=At.PIFtarget.list2)
    GO.ORA.temp.up_up<-GOseq.At.customcat.ORA(as_vector(genelist.upup[,"gene_id"]),custom.category.list=At.PIFtarget.list2)
    GO.ORA.temp.up_down<-GOseq.At.customcat.ORA(as_vector(genelist.updown[,"gene_id"]),custom.category.list=At.PIFtarget.list2)
    GO.ORA.temp.down_up<-GOseq.At.customcat.ORA(as_vector(genelist.downup[,"gene_id"]),custom.category.list=At.PIFtarget.list2)
    GO.ORA.temp.down_down<-GOseq.At.customcat.ORA(as_vector(genelist.downdown[,"gene_id"]),custom.category.list=At.PIFtarget.list2)
 #   }
    # handling "no enriched GO" 
    # genelist.names<-c("GO.ORA.temp.up_down","GO.ORA.temp.down_up") # test
    x<-list(GO.ORA.temp.all=GO.ORA.temp.all,
      GO.ORA.temp.up_up=GO.ORA.temp.up_up,
            GO.ORA.temp.up_down=GO.ORA.temp.up_down,
            GO.ORA.temp.down_up=GO.ORA.temp.down_up,
            GO.ORA.temp.down_down=GO.ORA.temp.down_down) # list
    print(x[x=="no enriched GO"])
    x<-x[!x=="no enriched GO"] # reove "no enriched GO" result
    ## add sample info and FC info and save GO.ORA result (this is not working well; 072819)
    ## avoid error with x is empty
    if(length(x)==0) {next} else {
  for (i in 1:length(x)) {
      GO.ORA.result<-x[[i]] %>% mutate(FC = gsub("(GO.ORA.temp.)(.)","\\2",names(x)[i]),sample=DEG.objs[n])
    save(GO.ORA.result,file=file.path("..","output","doubleCoef",paste(gsub(".csv","",DEG.objs[n]),gsub("(GO.ORA.temp.)(.)","\\2",names(x)[i]),"enrich.Rdata",sep=".")))
    rm(GO.ORA.result)
  }
    } 
}

```

# read GOseq result table
```{r messages=FALSE}
eGOseqs<-list.files(pattern="enrich.Rdata",path=file.path("..","output","doubleCoef"))
eGOseqs.list2<-sapply(file.path("..","output","doubleCoef",eGOseqs),function(x) mget(load(x))) # mget will return the value of the object(or objects) in a list. see https://stackoverflow.com/questions/29398630/load-data-frames-into-list
#names(eGOseqs.list2)
eGOseqs.list2.summary<-do.call("rbind",eGOseqs.list2) 
#head(eGOseqs.list2.summary) # make sure those are file names
rownames(eGOseqs.list2.summary)<-1:nrow(eGOseqs.list2.summary)
View(eGOseqs.list2.summary)
# write in csv file
write_csv(eGOseqs.list2.summary,path=file.path("..","output","doubleCoef","PIFtarget.eGOseqs.list2.summary.v3.csv"))
```

# plotting expression pattern
```{r}
###import dge.data and calculate cpm
# fo Kazu
 if(Sys.info()["user"]=="nozue") { 
load(file.path("~","Box","Chunmei_Myc_Paper","manuscripts","output/dge.Rdata"))
 }
# for Chunmei
 if(Sys.info()["user"]=="LCM") { 
load(file.path("C:","Users","LCM","Box","Chunmei_Myc_Paper","manuscripts","output/dge.Rdata"))
 }

log2_cpm <- log2(cpm(dge.data)+1) # copied and pasted from "combined_scripts_for_figures.Rmd". Why log2(cpm(dge.data)+1)? not log2(cpm(dge.data))? (052319)
head(log2_cpm)
rownames(log2_cpm) <- gsub("\\.\\d", "", rownames(log2_cpm)) #remove ".digital" after each AGI number

#subset to keep Col and myc234 data

log2_cpm <- log2_cpm[, 1:32]
head(log2_cpm)
#
cpm.wide <- bind_cols(tibble(gene_id=rownames(log2_cpm)),as_tibble(log2_cpm)) 
cpm.wide
```
# plot ("up" in myc324 (logFC.gtmyc234>0))
```{r}
names(DEG.list)
# npr1-1 misregulated genes 
plot.data<-DEG.list[["DEgenes.myc234.49h.rCol.rH"]] %>% left_join(cpm.wide,by="gene_id") %>% unite(AGI_desc,c("gene_id","name")) %>% dplyr::select(-LR,-PValue,-X1,-logCPM) 
# plot: use labeller = label_wrap_gen(width=10) for multiple line in each gene name
p.up<-plot.data %>% filter(logFC.gtmyc234>0 & FDR<1e-10) %>% dplyr::select(-logFC.gtmyc234,-logFC.gtmyc234.trtL,-FDR,-description) %>%  gather(sample,value,-1) %>%
  separate(sample, into = c("genotype", "time_point", "treatment", "rep"), sep = "_") %>% ggplot(aes(x=fct_relevel(treatment,"H"),y=value,color=genotype,shape=rep)) + geom_jitter() + facet_wrap(AGI_desc~.,scale="free",ncol=5,labeller = label_wrap_gen(width=30))+theme(strip.text = element_text(size=6)) + labs(title="up (logFC.gtmyc234>0)")
p.up
```
# plot ("down" in myc324 (logFC.gtmyc234>0))
```{r}
names(DEG.list)
# npr1-1 misregulated genes 
plot.data<-DEG.list[["DEgenes.myc234.49h.rCol.rH"]] %>% left_join(cpm.wide,by="gene_id") %>% unite(AGI_desc,c("gene_id","name")) %>% dplyr::select(-LR,-PValue,-X1,-logCPM) 
# plot: use labeller = label_wrap_gen(width=10) for multiple line in each gene name
p.down<-plot.data %>% filter(logFC.gtmyc234<0 & FDR<1e-100) %>% dplyr::select(-logFC.gtmyc234,-logFC.gtmyc234.trtL,-FDR,-description) %>%  gather(sample,value,-1) %>%
  separate(sample, into = c("genotype", "time_point", "treatment", "rep"), sep = "_") %>% ggplot(aes(x=fct_relevel(treatment,"H"),y=value,color=genotype,shape=rep)) + geom_jitter() + facet_wrap(AGI_desc~.,scale="free",ncol=5,labeller = label_wrap_gen(width=30))+theme(strip.text = element_text(size=6)) + labs(title="down (logFC.gtmyc234<0)")
p.down
```
# plot "Col and myc234 at 49h high and low RFR" (requested by Julin on July 28, 2019). under construction
```{r}
names(DEG.list)
plot.data<-
  DEG.list[["DEgenes.Col.49h.rH"]] 
  DEG.list[["DEgenes.myc234.49h.rCol.rH"]] 

%>% left_join(cpm.wide,by="gene_id") %>% unite(AGI_desc,c("gene_id","name")) %>% dplyr::select(-LR,-PValue,-X1,-logCPM) 
# plot: use labeller = label_wrap_gen(width=10) for multiple line in each gene name
p.down<-plot.data %>% filter(logFC.gtmyc234<0 & FDR<1e-100) %>% dplyr::select(-logFC.gtmyc234,-logFC.gtmyc234.trtL,-FDR,-description) %>%  gather(sample,value,-1) %>%
  separate(sample, into = c("genotype", "time_point", "treatment", "rep"), sep = "_") %>% ggplot(aes(x=fct_relevel(treatment,"H"),y=value,color=genotype,shape=rep)) + geom_jitter() + facet_wrap(AGI_desc~.,scale="free",ncol=5,labeller = label_wrap_gen(width=30))+theme(strip.text = element_text(size=6)) + labs(title="down (logFC.gtmyc234<0)")
p.down
```

# expression pattern of overlapped genes between PIFtargets
# DEgenes.myc234.1h.rCol.rH
```{r}
plot.data.down_down<-DEG.list[["DEgenes.myc234.1h.rCol.rH"]] %>% left_join(cpm.wide,by="gene_id") %>% unite(AGI_desc,c("gene_id","name"),remove=FALSE) %>% dplyr::select(-LR,-PValue,-X1,-logCPM)  %>% filter(logFC.gtmyc234<0 & logFC.gtmyc234.trtL<0) 

# plot: use labeller = label_wrap_gen(width=10) for multiple line in each gene name
# p.myc234.49h.rCol.rH.down_down.PIFup
p.myc234.1h.rCol.rH.down_down.PIFcomplex<-plot.data.down_down %>% inner_join(tibble(gene_id=PIFcomplex),by="gene_id") %>%  dplyr::select(-logFC.gtmyc234,-logFC.gtmyc234.trtL,-FDR,-description,-gene_id,-name) %>%  gather(sample,value,-1) %>%
  separate(sample, into = c("genotype", "time_point", "treatment", "rep"), sep = "_") %>% ggplot(aes(x=fct_relevel(treatment,"H"),y=value,color=genotype,shape=rep)) + geom_jitter() + facet_wrap(AGI_desc~.,scale="free",ncol=5,labeller = label_wrap_gen(width=30))+theme(strip.text = element_text(size=6)) + labs(title="1h down_down \n(logFC.gtmyc234<0 & logFC.gtmyc234.trtL<0) \n& PIFcomplex")
p.myc234.1h.rCol.rH.down_down.PIFcomplex
ggsave(p.myc234.1h.rCol.rH.down_down.PIFcomplex,file=file.path("..","output","doubleCoef","p.myc234.1h.rCol.rH.down_down.PIFcomplex.png"),height=3,width=5)

```
# DEgenes.myc234.49h.rCol.rH down_down & PIFup
```{r}
plot.data.down_down<-DEG.list[["DEgenes.myc234.49h.rCol.rH"]] %>% left_join(cpm.wide,by="gene_id") %>% unite(AGI_desc,c("gene_id","name"),remove=FALSE) %>% dplyr::select(-LR,-PValue,-X1,-logCPM)  %>% filter(logFC.gtmyc234<0 & logFC.gtmyc234.trtL<0) 
# plot: use labeller = label_wrap_gen(width=10) for multiple line in each gene name
# p.myc234.49h.rCol.rH.down_down.PIFup
p.myc234.49h.rCol.rH.down_down.PIFup<-plot.data.down_down %>% inner_join(tibble(gene_id=PIFup),by="gene_id") %>%  dplyr::select(-logFC.gtmyc234,-logFC.gtmyc234.trtL,-FDR,-description,-gene_id,-name) %>%  gather(sample,value,-1) %>%
  separate(sample, into = c("genotype", "time_point", "treatment", "rep"), sep = "_") %>% ggplot(aes(x=fct_relevel(treatment,"H"),y=value,color=genotype,shape=rep)) + geom_jitter() + facet_wrap(AGI_desc~.,scale="free",ncol=5,labeller = label_wrap_gen(width=30))+theme(strip.text = element_text(size=6)) + labs(title="down_down \n(logFC.gtmyc234<0 & logFC.gtmyc234.trtL<0) \n& PIFup")
p.myc234.49h.rCol.rH.down_down.PIFup
ggsave(p.myc234.49h.rCol.rH.down_down.PIFup,file=file.path("..","output","doubleCoef","p.myc234.49h.rCol.rH.down_down.PIFup.png"),height=3,width=8)

```
# p.myc234.49h.rCol.rH.up_down.PIFcomplex
```{r}
# up_down
plot.data.up_down<-DEG.list[["DEgenes.myc234.49h.rCol.rH"]] %>% left_join(cpm.wide,by="gene_id") %>% unite(AGI_desc,c("gene_id","name"),remove=FALSE) %>% dplyr::select(-LR,-PValue,-X1,-logCPM)  %>% filter(logFC.gtmyc234>0 & logFC.gtmyc234.trtL<0) 
# plot
p.myc234.49h.rCol.rH.up_down.PIFcomplex<-plot.data.up_down %>% inner_join(tibble(gene_id=PIFcomplex),by="gene_id") %>%  dplyr::select(-logFC.gtmyc234,-logFC.gtmyc234.trtL,-FDR,-description,-gene_id,-name) %>%  gather(sample,value,-1) %>%
  separate(sample, into = c("genotype", "time_point", "treatment", "rep"), sep = "_") %>% ggplot(aes(x=fct_relevel(treatment,"H"),y=value,color=genotype,shape=rep)) + geom_jitter() + facet_wrap(AGI_desc~.,scale="free",ncol=5,labeller = label_wrap_gen(width=30))+theme(strip.text = element_text(size=6)) + labs(title="up_down \n(logFC.gtmyc234>0 & logFC.gtmyc234.trtL<0) \n& PIFcomplex")
p.myc234.49h.rCol.rH.up_down.PIFcomplex
ggsave(p.myc234.49h.rCol.rH.up_down.PIFcomplex,file=file.path("..","output","doubleCoef","p.myc234.49h.rCol.rH.up_down.PIFcomplex.png"),height=3,width=5)
```


# Session info
```{r}
sessionInfo()
```